\documentclass[t]{beamer}

\setlength {\marginparwidth }{2cm} 
\usepackage{todonotes}
\usepackage{siunitx}
\usepackage{subcaption}
\usepackage{apacite} 	% Use APA Citation
\presetkeys{todonotes}{inline}{}
\beamertemplatenavigationsymbolsempty

\usepackage{enumitem}

% \usetheme{AnnArbor}
% \usetheme{Antibes}
% \usetheme{Bergen}
% \usetheme{Berkeley}https://www.sharelatex.com/project/5b12e1a4f84b363f6f336dab
% \usetheme{Berlin}
% \usetheme{Boadilla}
% \usetheme{boxes}
\usetheme{CambridgeUS}
% \usetheme{Copenhagen}
%\usetheme{Darmstadt}
% \usetheme{default}
%\usetheme{Frankfurt}
%\usetheme{Goettingen}
% \usetheme{Hannover}
% \usetheme{Ilmenau}
% \usetheme{JuanLesPins}
\setlength{\parskip}{10pt}

% \newcommand*\vc[1]%
% {\begin{pmatrix}#1\end{pmatrix}}

\newcommand*\vc[1]%
{\left(\begin{array}{cccc}#1\end{array}\right)}


\newcommand\eqdef{\ \mathrel{\overset{\makebox[0pt]{\mbox{\normalfont\scriptsize\sffamily def}}}{=}}\ }

\title[Eligibility propagation]{Improving eligibility propagation using Izhikevich neurons in a multilayer RSNN.\\\vspace{10pt}
\large{Presentation 2: Visualization, validating, and visualization}}

\author[Werner]{Werner~van~der~Veen\\\tiny\texttt({w.k.van.der.veen.2@umcg.nl})}\date{\today}

\begin{document}

\begin{frame}
    \titlepage
\end{frame}

%======================================

\small
\section{Work done}

\begin{frame}{Work done}
	\begin{itemize}
		\item Visualization:
			\begin{itemize}
				\item Network graph;
				\item Full state history \& IO plot.
			\end{itemize}
		\item Validation:
			\begin{itemize}
				\item New tasks: pulse, sinusoid, NARMA-10;
				\item Identified and fixed a number of errors;
				\item Replaced EMA by $W_{out}$.
				
			\end{itemize}
		\item Major refactor and cleaning of code.
		\item Better study and increased understanding of e-prop algorithm.
	\end{itemize}
\end{frame}

\begin{frame}{Still to do}
    \textbf{Next steps:}
    
    1. Acquire results of NARMA-10 benchmark.
    
    2. Implement adaptive e-prop: learning signal mapped back onto weights through learnable regression weights. Currently using static weights.
    
    3. Reproduce Bellec's TIMIT performance.
\end{frame}

\begin{frame}{Questions}
    1. Implementing synaptic scaling was one of the proposed improvements to the network, but ALIF neurons effectively incorporate this. Should I stay with ALIF, or implement SS in Izhikevich neurons?
\end{frame}

\end{document}
