\documentclass[t]{beamer}

\setlength {\marginparwidth }{2cm} 
\usepackage{todonotes}
\usepackage{siunitx}
\usepackage{subcaption}
\usepackage{apacite} 	% Use APA Citation
\presetkeys{todonotes}{inline}{}
\beamertemplatenavigationsymbolsempty

\usepackage{algpseudocode}
\usepackage{enumitem,amssymb, yfonts}
\newlist{todolist}{itemize}{2}
\setlist[todolist]{label=$\square$}
\usepackage{pifont}
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%
\newcommand{\done}{\rlap{$\square$}{\raisebox{2pt}{\large\hspace{1pt}\cmark}}%
\hspace{-2.5pt}}

% \usetheme{AnnArbor}
% \usetheme{Antibes}
% \usetheme{Bergen}
% \usetheme{Berkeley}https://www.sharelatex.com/project/5b12e1a4f84b363f6f336dab
% \usetheme{Berlin}
% \usetheme{Boadilla}
% \usetheme{boxes}
\usetheme{CambridgeUS}
% \usetheme{Copenhagen}
%\usetheme{Darmstadt}
% \usetheme{default}
%\usetheme{Frankfurt}
%\usetheme{Goettingen}
% \usetheme{Hannover}
% \usetheme{Ilmenau}
% \usetheme{JuanLesPins}
\setlength{\parskip}{10pt}

% \newcommand*\vc[1]%
% {\begin{pmatrix}#1\end{pmatrix}}

\newcommand*\vc[1]%
{\left(\begin{array}{cccc}#1\end{array}\right)}


\newcommand\eqdef{\ \mathrel{\overset{\makebox[0pt]{\mbox{\normalfont\scriptsize\sffamily def}}}{=}}\ }

\title[Eligibility propagation]{Improving eligibility propagation using Izhikevich neurons in a multilayer RSNN.\\\vspace{10pt}
\large{Presentation 4: A bidirectional crossroads}}

\author[Werner]{Werner~van~der~Veen\\\tiny\texttt({w.k.van.der.veen.2@student.rug.nl})}\date{\today}

% \pgfdeclareimage[height=1cm]{umcg-logo}{umcg.png}
% \newif\ifplacelogo
% \placelogotrue
% \logo{\ifplacelogo\pgfuseimage{umcg-logo}\fi}

\begin{document}

\begin{frame}
    \titlepage
\end{frame}

%======================================

%\begin{frame}
%    \tableofcontents
%\end{frame}

\small
\section{Work done since previous meeting}
\begin{frame}{Work done since previous meeting}
	\begin{todolist}

    \item[\done] Implement Bellec's tricks. Should be able to reproduce thereafter:
    \begin{todolist}
    	\item[\done] L2 \& firing rate regularization
    	\item[\done] Firing rate regularization
    	\item[\done] Gaussian distribution for broadcast weights
    	\item[\done] Adam optimizer
    \end{todolist}
    \item \textbf{Bidirectional network} (?)
    \item Obtain Bellec's performance.
    \item Experiment with my own tweaks (e.g. multi-layered).
  \end{todolist}
\end{frame}

\section{Current system performance}
\begin{frame}{Current system performance}
	
	\begin{itemize}[label=--]
	\item Training with bias or output weights: converges to single output.
	\item Training with only recurrent weights: converges little bit but not meaningful.
	\item \textbf{But:} when disabling weight decay and L2, no more convergence.
	\end{itemize}
\end{frame}


\begin{frame}{Questions}
	\begin{itemize}[label=--]
	\item Only difference: bidirectionality.\\Pros: closer to Bellec.\\Cons: no good reason, no bioplausibility, no online learning.\\
	\item Q1: Bidirectional network: is my understanding correct? Switch target sequence too?
	\item Q2: Should I implement it, or try to maximize performance on unidirectional?
	\item Q3: Further suggestions on how to proceed, based on current performance?
	\item Q4: Weights in network?
	\end{itemize}
\end{frame}



\end{document}
