\documentclass[t]{beamer}

\setlength {\marginparwidth }{2cm}
\setlength {\parskip}{0cm}
\usepackage{todonotes}
\usepackage{siunitx}
\usepackage{subcaption}
\usepackage{apacite}    % Use APA Citation
\presetkeys{todonotes}{inline}{}
\beamertemplatenavigationsymbolsempty
\usefonttheme[onlymath]{serif}

\usepackage{algpseudocode}
\usepackage{enumitem,amssymb, yfonts, bm}
\newlist{todolist}{itemize}{2}
\setlist[todolist]{label=$\square$}
\usepackage{pifont}
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%
\newcommand{\done}{\rlap{$\square$}{\raisebox{2pt}{\large\hspace{1pt}\cmark}}%
\hspace{-2.5pt}}

% \usetheme{AnnArbor}
% \usetheme{Antibes}
% \usetheme{Bergen}
% \usetheme{Berkeley}https://www.sharelatex.com/project/5b12e1a4f84b363f6f336dab
% \usetheme{Berlin}
% \usetheme{Boadilla}
% \usetheme{boxes}
\usetheme{CambridgeUS}
% \usetheme{Copenhagen}
%\usetheme{Darmstadt}
% \usetheme{default}
%\usetheme{Frankfurt}
%\usetheme{Goettingen}
% \usetheme{Hannover}
% \usetheme{Ilmenau}
% \usetheme{JuanLesPins}
\setlength{\parskip}{10pt}

% \newcommand*\vc[1]%
% {\begin{pmatrix}#1\end{pmatrix}}

\newcommand*\vc[1]%
{\left(\begin{array}{cccc}#1\end{array}\right)}


\newcommand\eqdef{\ \mathrel{\overset{\makebox[0pt]{\mbox{\normalfont\scriptsize\rmfamily def}}}{=}}\ }

\title[Eligibility propagation]{Improving eligibility propagation using Izhikevich neurons in a multilayer RSNN.\\\vspace{10pt}
\large{Presentation 7: Reproducing Bellec}}

\author[Werner]{Werner~van~der~Veen\\\footnotesize\texttt({w.k.van.der.veen.2@student.rug.nl})}\date{\today}

\begin{document}

\begin{frame}
    \titlepage
\end{frame}

%======================================

%\begin{frame}
%    \tableofcontents
%\end{frame}

\small

\section{Work done since previous meeting}
\begin{frame}{Work done since previous meeting}
  \begin{todolist}

    \item[\done] Identified and fixed errors.
    \item[\done] Rewrote system on GPU, now 10x faster.

  \end{todolist}

\end{frame}

\section{Work done since previous meeting}
\begin{frame}{Work done since previous meeting}
  \begin{itemize}[label=--]

    \item Bellec uses iteration-based training.\\
    $\rightarrow$ 80 epochs $\times$ 116 batches of size 32.
    \item My system trains correctly, but not at the same speed and stability as Bellec's.
    $\rightarrow$ Likely a mistake somewhere in the system.

  \end{itemize}

\end{frame}

\section{Current system}
\begin{frame}{}
  (show figures)
  \begin{itemize}[label=--]

    \item Some weights decrease a lot $\rightarrow$ maybe matrix shape error?
    \item Underfitting (logically)
    \item Bias and output layer train correctly
    \item Bellec reaches 30\% accuracy in 10 minutes, I do in 10 hours.
    \item Bellec

  \end{itemize}

\end{frame}

\begin{frame}{Current plan}
  \begin{itemize}[label=--]

    \item Backtrack the error, look first into weight/gradient shapes.
    \item E-mail the e-prop team for anything unreported in their paper.
    $\rightarrow$ initialization, learning curves, and a number of technical aspects.
  \end{itemize}
\end{frame}

\end{document}
