%************************************************
\chapter{Conclusion}\label{ch:conclusion}
%************************************************

As deep learning models require increasing amount of energy, the upcoming neuromorphic computing paradigm offers various ways to more efficiently run spiking neural networks.
Spiking neural networks can learn to perform tasks with a good performance and low energy requirements, but there is no established learning algorithm yet.
In this paper, the e-prop learning algorithm for recurrent spiking neural networks was combined with STDP, which is a major component of biological learning.

In this report, the e-prop framework was applied on the TIMIT phone classification task, meeting the objectives listed in Chapter \ref{ch:introduction}.
First, the performance of the ALIF neuron was reproduced using the explicit e-prop equations.
Next, the STDP-LIF neuron was modified to the STDP-ALIF model that was experimentally verified to outperform the ALIF neuron on the TIMIT learning task.
Also, the Izhikevich neuron, which also shows STDP behavior, was shown to be unstable and performing worse than the ALIF and STDP-ALIF neurons.
This suggests that STDP does not provide an adequate neuron model by itself, but that e.g. spike frequency adaptation also needs to be taken into account.

Finally, the effect of stacking multiple layers was also examined in combination with the ALIF, STDP-ALIF, and Izhikevich neuron model, and did not appear to improve the learning performance in this task.

Possible future work on this topic includes research on the effects of more elaborate weight initialization methods, variable hyperparameters for individual neurons, different static or dynamic connectivity graphs, and synaptic delays.

The scientific gain of this research is that the link between STDP and e-prop was more closely examined than in previous literature, and that the inclusion of STDP in e-prop can lead to a more accurate or efficient learning performance.
E-prop, particularly paired with the STDP-ALIF neuron model, remains a framework that offers high potential for biologically plausible learning algorithms for SNNs, which can be particularly well-suited for replicating intelligent behavior in low-power neuromorphic hardware.

